Pigeons.jl: Distributed sampling from intractable distributions

### 2023-11-01 paper/header.tex
try debug

\author[1]{Nikola Surjanovic}
\author[1]{Miguel Biron-Lattes}
\author[2]{Paul Tiede}
\author[3]{Saifuddin Syed}
\author[1]{Trevor Campbell}
\author[1]{Alexandre Bouchard-Côté}
\affil[1]{University of British Columbia}
\affil[2]{Harvard University}
\affil[3]{University of Oxford}

@@

\hypersetup{
pdftitle = {Pigeons.jl: Distributed sampling from intractable distributions},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Nikola Surjanovic, Miguel Biron-Lattes, Paul Tiede, Saifuddin Syed, Trevor Campbell, Alexandre Bouchard-Côté},
pdfkeywords = {distributed computation, Bayesian inference, parallelism invariance, multi-threading, Message Passing Interface, Markov chain Monte Carlo},
}

>>>>

\author[1]{Nikola Surjanovic}
\author[1]{Miguel Biron-Lattes}
\author[2]{Paul Tiede}
\author[3]{Saifuddin Syed}
\author[1]{Trevor Campbell}
\author[1]{Alexandre Bouchard-C\^{o}t\'{e}}
\affil[1]{University of British Columbia}
\affil[2]{Harvard University}
\affil[3]{University of Oxford}

@@

\hypersetup{
pdftitle = {Pigeons.jl: Distributed sampling from intractable distributions},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Nikola Surjanovic, Miguel Biron-Lattes, Paul Tiede, Saifuddin Syed, Trevor Campbell, Alexandre Bouchard-C\^{o}t\'{e}},
pdfkeywords = {distributed computation, Bayesian inference, parallelism invariance, multi-threading, Message Passing Interface, Markov chain Monte Carlo},
}
